### 2021-04-09 ch05_paper_ecs/paper_ecs.tex
Fixed usage of numerals (follolwing APA style)

One of the most important sources of information for this purpose is
undoubtedly observational data. As presented in
\cref{subsec:02:emergent_constraints}, appropriate observations of the Earth
system can be utilized within the so-called \emph{emergent constraints}
framework to assess the accuracy of climate model projections and reduce
associated uncertainties. For \ac{ECS}, a large variety of different emergent
constraints have been developed over the years, which we now evaluate on the
\acs{CMIP}6 ensemble to assess whether they still hold for these new climate
models, \ie{} whether they have skill to reduce uncertainties in \ac{ECS} in
the \acs{CMIP}6 ensemble. In total we assess eleven emergent constraints on
\ac{ECS} (see \cref{tab:05:overview_emergent_constraints}), out of which the
most are related to cloud feedbacks since these constitute the most important
source of uncertainty for \ac{ECS} \commentcite{Boucher2013, Flato2013}{see
  also \cref{subsec:02:climate_feedbacks}}. Since all of the evaluated emergent
constraints have been derived from the \acs{CMIP}3 or \acs{CMIP}5 ensemble, the
\acs{CMIP}6 models offer an exciting possibility to perform out-of-sample
testing using the previously unseen data.

\begin{table}[!t]
  \centering
  \hbadness=3500
  \begin{tabular}{p{0.07\columnwidth} p{0.24\columnwidth} p{0.29\columnwidth}
      p{0.29\columnwidth}}
    \toprule
    Label & Reference & Description of \xaxis{} & Variables and corresponding
    observations \\
    \midrule
    BRI & \textcite{Brient2016} & Sensitivity of shortwave cloud albedo
    to changes in \acf{SST} [$\si{\pctK{}}$] & \makecell{\tabitem\emph{hur}
      (ERA-Interim) \\ \tabitem \emph{rsdt} (CERES-EBAF) \\ \tabitem
      \emph{rsut} (CERES-EBAF) \\ \tabitem \emph{rsutcs} (CERES-EBAF) \\
      \tabitem \emph{ts} (HadISST)} \\
    \midrule
    COX & \textcite{Cox2018} & $\Psi$ (temperature variability metric)
    [$\si{K}$] &
    \tabitem \emph{tas} (HadCRUT4) \\
    \midrule
    LIP & \textcite{Lipat2017} & Extent of Southern Hemisphere Hadley cell
    [$\si{\degree}$] & \tabitem \emph{va} (ERA-Interim) \\
    \midrule
    SHD & \textcite{Sherwood2014} & $D$-index (large-scale lower-tropospheric
    mixing) [$\si{1}$] & \tabitem \emph{wap} (ERA-Interim) \\
    \midrule
    SHL & \textcite{Sherwood2014} & \acs{LTMI} (\acl{LTMI}) [$\si{1}$] &
    \makecell{\tabitem \emph{hur} (ERA-Interim) \\ \tabitem \emph{ta}
      (ERA-Interim) \\ \tabitem \emph{wap} (ERA-Interim)} \\
    \midrule
    SHS & \textcite{Sherwood2014} & $S$-index (small-scale lower-tropospheric
    mixing) [$\si{1}$] & \makecell{\tabitem \emph{hur} (ERA-Interim) \\
      \tabitem \emph{ta} (ERA-Interim) \\ \tabitem \emph{wap} (ERA-Interim)} \\
    \midrule
    SU & \textcite{Su2014} & Error in vertical profile of relative humidity
    [$\si{1}$] & \tabitem \emph{hur} (AIRS, MLS-Aura) \\
    \midrule
    TIH & \textcite{Tian2015} & Tropical mid-tropospheric humidity asymmetry
    index from AIRS [$\si{\%}$] & \tabitem \emph{hus} (AIRS) \\
    \midrule
    TII & \textcite{Tian2015} & Southern \acs{ITCZ} index from GPCP
    [$\si{\mmday{}}$] & \tabitem \emph{pr} (GPCP) \\
    \midrule
    VOL* & \textcite{Volodin2008} & Difference between tropical and southern
    midlatitudinal cloud fraction [$\si{\%}$] & \tabitem \emph{clt} (ISCCP
    D-2) \\
    \midrule
    ZHA* & \textcite{Zhai2015} & Seasonal response of \acl{MBLC} fraction to
    changes in \acs{SST} [$\si{\pctK{}}$] &
    \makecell{\tabitem \emph{cl} (CloudSat/CALIPSO) \\ \tabitem \emph{tos}
      (AMSRE \acs{SST}) \\ \tabitem \emph{wap} (ERA-Interim)} \\
    \bottomrule
  \end{tabular}
  \caption[
    Overview of the eleven emergent constraints on the \acf{ECS} evaluated in
    \cref{ch:05:paper_ecs}.
  ]{
    Overview of the eleven emergent constraints on the \acf{ECS} evaluated in
    this \namecref{ch:05:paper_ecs}. Detailed descriptions of the variables
    used to calculate the \xaxis{} values of the emergent constraints and the
    references for the corresponding observations (fourth column) are given in
    \cref{tab:app:a:overview_variables,tab:app:a:observations}, respectively.
    For emergent constraints marked with an asterisk (*), the observational
    value of the original publication is used to calculate the observational
    constraint. For all others, the observational value is computed with the
    \acs{ESMValTool}. \AdaptedFrom{Schlund2020a}.
  }
  \label{tab:05:overview_emergent_constraints}
\end{table}

This work is already published in \textcite{Schlund2020a}. For this paper, the
author of this thesis led the writing and the analysis and implemented the code
to reproduce this study with all figures and tables using the \ac{ESMValTool}.
In this \namecref{ch:05:paper_ecs}, we first introduce the data (climate model
output and observations) and methods used in this study
(\cref{sec:05:data_and_methods}). After that, we present the eleven emergent
constraints on \acs{ECS} and evaluate them on the \acs{CMIP}5 and \acs{CMIP}6
ensemble (\cref{sec:05:comparison_of_emergent_constraints}). Finally, we
provide a discussion (\cref{sec:05:discussion}) and a summary of the results
(\cref{sec:05:summary}).

@@

In this study we use the output from climate models participating in
\acs{CMIP}5 and \acs{CMIP}6 as shown in
\cref{tab:app:a:cmip5_models,tab:app:a:cmip6_models}, respectively. In
addition, for each emergent constraint at least one observational dataset is
used to calculate the observational constraint. A complete list of these
datasets is given in \cref{tab:05:overview_emergent_constraints} and in
\cref{tab:app:a:observations}. Following other similar studies, we calculate
\ac{ECS} with the Gregory regression method \autocite{Gregory2004}, which is
described in detail in \cref{subsec:02:ecs}. An overview of the eleven emergent
constraints on \ac{ECS} analyzed in this study including the variables required
for their calculations is given in \cref{tab:05:overview_emergent_constraints}
and \cref{sec:05:comparison_of_emergent_constraints}. We chose these particular
emergent constraints since these had already been implemented in the
\ac{ESMValTool} at the time of writing this study, which greatly facilitated
this analysis. For all emergent constraints, we use the historical simulations
of \acs{CMIP}5 and \acs{CMIP}6 to ensure maximum agreement with the
observational data. If necessary, the historical simulation of \acs{CMIP}5 is
extended after its final year 2005 with data from the \acs{RCP}8.5 scenario
\autocite{Riahi2011}. Note that we only use data through 2014, during which
time all \ac{RCP} scenarios behave similarly and the choice of the scenario is
not expected to affect the results considerably. Such an extension is not
needed for \acs{CMIP}6 models as their historical simulations cover a longer
time period until 2014. We quantify the skill of the emergent constraints with
three metrics: the coefficient of determination $R^2$ of the linear
relationship, the statistical significance using a two-sided $t$-test based on
the Pearson correlation coefficient $r$ (see \cref{eq:02:t}), and the
constrained range of \ac{ECS} based on the constrained \ac{PDF} (see
\cref{eq:02:pdf_y_given_x0}).

@@

In this \namecref{sec:05:comparison_of_emergent_constraints} we describe and
discuss the eleven emergent constraints on \ac{ECS} summarized in
\cref{tab:05:overview_emergent_constraints} using \acs{CMIP}5 and \acs{CMIP}6
data
(\cref{subsec:05:bri,subsec:05:cox,subsec:05:lip,subsec:05:shd,subsec:05:shs,%
  subsec:05:shl,subsec:05:su,subsec:05:tih,subsec:05:tii,subsec:05:vol,%
  subsec:05:zha}) and provide a best estimate for \ac{ECS} and statistical
significance of the eleven emergent constraints in
\cref{subsec:05:emergent_constraints_summary}. While most of these emergent
constraints have been derived using data from the \acs{CMIP}5 and/or
\acs{CMIP}3 ensembles, to our knowledge none of them has been evaluated on
the \acs{CMIP}6 ensemble so far. The results for the individual emergent
constraints described in the following are shown in
\cref{fig:05:bri_cox_lip,fig:05:shd_shl_shs,fig:05:su_tih_tii,fig:05:vol_zha}.
The left columns in these figures show the emergent relationships, including
the uncertainty of the linear regressions (blue and orange shaded areas; see
\cref{eq:02:spe}) and the uncertainty in the observations (gray shaded area;
see \cref{eq:02:pdf_obs}). The right columns show the \acp{PDF} of \ac{ECS} in
the original model ensemble (histogram) and the constrained distribution given
by the emergent constraints (blue and orange line; see
\cref{eq:02:pdf_y_given_x0}). \Cref{tab:05:overview_results} shows the
corresponding $66 \unit{\%}$ confidence intervals (\ie{} the
$\rangeunit{17}{83}{\%}$ intervals) of \ac{ECS} derived from the \acp{PDF}
given by \cref{eq:02:pdf_y_given_x0} and the $p$-values used to assess the
significance of the emergent relationships.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{ch05_paper_ecs/figs/zha.pdf}
  \caption[
    Emergent relationship ZHA for different subsets of \acs{CMIP}5 models.
  ]{
    Emergent relationship ZHA \autocite{Zhai2015} for different subsets of
    \acs{CMIP}5 models. Blue circles show the 15 \acs{CMIP}5 models used in the
    original publication (except for \acs{CESM}1-CAM5). The solid blue line and
    blue shaded area show the emergent relationships evaluated on these models
    including the uncertainty range. In our study, we added eleven more
    \acs{CMIP}5 models (red circles). The corresponding emergent relationship
    that considers all available \acs{CMIP}5 models is shown in red colors.
    This relationship shows a considerably lower coefficient of determination
    ($R^2$) and higher $p$-value than the relationship using the original
    subset of \acs{CMIP}5 models. The vertical dashed line and shaded area
    correspond to the observational reference, and the horizontal dashed lines
    show the corresponding constraints on the \acf{ECS} using this observation.
    \AdaptedFrom{Schlund2020a}.
  }
  \label{fig:05:zha}
\end{figure}

\textcite{Zhai2015} focus on the variations of \acp{MBLC}, which largely
contribute to the shortwave cloud feedback and thus to the uncertainty in
modeled \ac{ECS}. Their central quantity is the response of the \ac{MBLC}
fraction to changes in the \ac{SST} in subtropical oceanic subsidence regions
for both hemispheres ($\rangeunit{20}{40}{\degree}$). On short (seasonal) and
long (centennial under a forcing) time scales, this quantity is well correlated
with \ac{ECS} among an ensemble of \acs{CMIP}3 and \acs{CMIP}5 models. Together
with observations of cloud fraction from CloudSat/CALIPSO \autocite{Mace2009},
\ac{SST} from AMSRE \ac{SST} \autocite{AMSRE2011}, and vertical velocity from
ERA-Interim \autocite{Dee2011}, the seasonal response of \ac{MBLC} fraction to
changes in \ac{SST} forms an emergent constraint on \ac{ECS}. We assess a $66
\unit{\%}$ \ac{ECS} range of $\pmrangeunit{3.35}{0.74}{K}$ for \acs{CMIP}5
($R^2 = 0.05$) and $\pmrangeunit{3.79}{0.67}{K}$ for \acs{CMIP}6 ($R^2 =
0.62$). In their original publication, \textcite{Zhai2015} find \iac{ECS} range
of $\pmrangeunit{3.90}{0.45}{K}$ (standard deviation) for a combination of
\acs{CMIP}3 and \acs{CMIP}5 models. In terms of statistical significance, the
results of the ZHA constraints are somewhat surprising: although \acs{CMIP}5
data (in combination with \acs{CMIP}3 data) has successfully been used in the
original publication, our approach finds that the statistical significance of
the emergent relationship is much higher in the unseen \acs{CMIP}6 ensemble ($p
< 0.0001$) than in the previously available \acs{CMIP}5 ensemble ($p =
0.2567$). The ZHA constraint is the only emergent constraint analyzed here that
shows this extreme behavior (only one other constraint, SHS, shows a slightly
higher significance in \acs{CMIP}6; all other constraints show lower
significances in \acs{CMIP}6). The reason for the erratic skill in \acs{CMIP}5
is the set of climate models used. For our analysis, we use eleven additional
\acs{CMIP}5 models that have not been used in the original publication
(ACCESS1-0, ACCESS1-3, bcc-csm1-1, bcc-csm1-1-m, CCSM4, GFDL-ESM2G, GFDL-ESM2M,
IPSL-CM5A-MR, IPSL-CM5B-LR, MPI-ESM-MR, and MPI-ESM-P). Due to a lack of
publicly available data, the model \acs{CESM}1-CAM5 that is used in the
original publication is not included in our analysis. The effect of choosing
different subsets of \acs{CMIP}5 models on the emergent relationship is
illustrated in \cref{fig:05:zha}. Using the original \acs{CMIP}5 models from
the original publication gives a considerably higher correlation ($R^2 = 0.38$)
than using all available \acs{CMIP}5 models ($R^2 = 0.05$). This result shows a
strong dependency of this emergent constraint on the subset of climate models
used. Nonetheless, the performance on \acs{CMIP}6 models is, surprisingly, the
best of all the constraints and much better than on either subset of
\acs{CMIP}5 models.

\subsection{Constrained \acs{ECS} Ranges and Statistical Significance of the
  Eleven Emergent Constraints}
\label{subsec:05:emergent_constraints_summary}

>>>>

One of the most important sources of information for this purpose is
undoubtedly observational data. As presented in
\cref{subsec:02:emergent_constraints}, appropriate observations of the Earth
system can be utilized within the so-called \emph{emergent constraints}
framework to assess the accuracy of climate model projections and reduce
associated uncertainties. For \ac{ECS}, a large variety of different emergent
constraints have been developed over the years, which we now evaluate on the
\acs{CMIP}6 ensemble to assess whether they still hold for these new climate
models, \ie{} whether they have skill to reduce uncertainties in \ac{ECS} in
the \acs{CMIP}6 ensemble. In total we assess 11 emergent constraints on
\ac{ECS} (see \cref{tab:05:overview_emergent_constraints}), out of which the
most are related to cloud feedbacks since these constitute the most important
source of uncertainty for \ac{ECS} \commentcite{Boucher2013, Flato2013}{see
  also \cref{subsec:02:climate_feedbacks}}. Since all of the evaluated emergent
constraints have been derived from the \acs{CMIP}3 or \acs{CMIP}5 ensemble, the
\acs{CMIP}6 models offer an exciting possibility to perform out-of-sample
testing using the previously unseen data.

\begin{table}[!t]
  \centering
  \hbadness=3500
  \begin{tabular}{p{0.07\columnwidth} p{0.24\columnwidth} p{0.29\columnwidth}
      p{0.29\columnwidth}}
    \toprule
    Label & Reference & Description of \xaxis{} & Variables and corresponding
    observations \\
    \midrule
    BRI & \textcite{Brient2016} & Sensitivity of shortwave cloud albedo
    to changes in \acf{SST} [$\si{\pctK{}}$] & \makecell{\tabitem\emph{hur}
      (ERA-Interim) \\ \tabitem \emph{rsdt} (CERES-EBAF) \\ \tabitem
      \emph{rsut} (CERES-EBAF) \\ \tabitem \emph{rsutcs} (CERES-EBAF) \\
      \tabitem \emph{ts} (HadISST)} \\
    \midrule
    COX & \textcite{Cox2018} & $\Psi$ (temperature variability metric)
    [$\si{K}$] &
    \tabitem \emph{tas} (HadCRUT4) \\
    \midrule
    LIP & \textcite{Lipat2017} & Extent of Southern Hemisphere Hadley cell
    [$\si{\degree}$] & \tabitem \emph{va} (ERA-Interim) \\
    \midrule
    SHD & \textcite{Sherwood2014} & $D$-index (large-scale lower-tropospheric
    mixing) [$\si{1}$] & \tabitem \emph{wap} (ERA-Interim) \\
    \midrule
    SHL & \textcite{Sherwood2014} & \acs{LTMI} (\acl{LTMI}) [$\si{1}$] &
    \makecell{\tabitem \emph{hur} (ERA-Interim) \\ \tabitem \emph{ta}
      (ERA-Interim) \\ \tabitem \emph{wap} (ERA-Interim)} \\
    \midrule
    SHS & \textcite{Sherwood2014} & $S$-index (small-scale lower-tropospheric
    mixing) [$\si{1}$] & \makecell{\tabitem \emph{hur} (ERA-Interim) \\
      \tabitem \emph{ta} (ERA-Interim) \\ \tabitem \emph{wap} (ERA-Interim)} \\
    \midrule
    SU & \textcite{Su2014} & Error in vertical profile of relative humidity
    [$\si{1}$] & \tabitem \emph{hur} (AIRS, MLS-Aura) \\
    \midrule
    TIH & \textcite{Tian2015} & Tropical mid-tropospheric humidity asymmetry
    index from AIRS [$\si{\%}$] & \tabitem \emph{hus} (AIRS) \\
    \midrule
    TII & \textcite{Tian2015} & Southern \acs{ITCZ} index from GPCP
    [$\si{\mmday{}}$] & \tabitem \emph{pr} (GPCP) \\
    \midrule
    VOL* & \textcite{Volodin2008} & Difference between tropical and southern
    midlatitudinal cloud fraction [$\si{\%}$] & \tabitem \emph{clt} (ISCCP
    D-2) \\
    \midrule
    ZHA* & \textcite{Zhai2015} & Seasonal response of \acl{MBLC} fraction to
    changes in \acs{SST} [$\si{\pctK{}}$] &
    \makecell{\tabitem \emph{cl} (CloudSat/CALIPSO) \\ \tabitem \emph{tos}
      (AMSRE \acs{SST}) \\ \tabitem \emph{wap} (ERA-Interim)} \\
    \bottomrule
  \end{tabular}
  \caption[
    Overview of the 11 emergent constraints on the \acf{ECS} evaluated in
    \cref{ch:05:paper_ecs}.
  ]{
    Overview of the 11 emergent constraints on the \acf{ECS} evaluated in this
    \namecref{ch:05:paper_ecs}. Detailed descriptions of the variables used to
    calculate the \xaxis{} values of the emergent constraints and the
    references for the corresponding observations (fourth column) are given in
    \cref{tab:app:a:overview_variables,tab:app:a:observations}, respectively.
    For emergent constraints marked with an asterisk (*), the observational
    value of the original publication is used to calculate the observational
    constraint. For all others, the observational value is computed with the
    \acs{ESMValTool}. \AdaptedFrom{Schlund2020a}.
  }
  \label{tab:05:overview_emergent_constraints}
\end{table}

This work is already published in \textcite{Schlund2020a}. For this paper, the
author of this thesis led the writing and the analysis and implemented the code
to reproduce this study with all figures and tables using the \ac{ESMValTool}.
In this \namecref{ch:05:paper_ecs}, we first introduce the data (climate model
output and observations) and methods used in this study
(\cref{sec:05:data_and_methods}). After that, we present the 11 emergent
constraints on \acs{ECS} and evaluate them on the \acs{CMIP}5 and \acs{CMIP}6
ensemble (\cref{sec:05:comparison_of_emergent_constraints}). Finally, we
provide a discussion (\cref{sec:05:discussion}) and a summary of the results
(\cref{sec:05:summary}).

@@

In this study we use the output from climate models participating in
\acs{CMIP}5 and \acs{CMIP}6 as shown in
\cref{tab:app:a:cmip5_models,tab:app:a:cmip6_models}, respectively. In
addition, for each emergent constraint at least one observational dataset is
used to calculate the observational constraint. A complete list of these
datasets is given in \cref{tab:05:overview_emergent_constraints} and in
\cref{tab:app:a:observations}. Following other similar studies, we calculate
\ac{ECS} with the Gregory regression method \autocite{Gregory2004}, which is
described in detail in \cref{subsec:02:ecs}. An overview of the 11 emergent
constraints on \ac{ECS} analyzed in this study including the variables required
for their calculations is given in \cref{tab:05:overview_emergent_constraints}
and \cref{sec:05:comparison_of_emergent_constraints}. We chose these particular
emergent constraints since these had already been implemented in the
\ac{ESMValTool} at the time of writing this study, which greatly facilitated
this analysis. For all emergent constraints, we use the historical simulations
of \acs{CMIP}5 and \acs{CMIP}6 to ensure maximum agreement with the
observational data. If necessary, the historical simulation of \acs{CMIP}5 is
extended after its final year 2005 with data from the \acs{RCP}8.5 scenario
\autocite{Riahi2011}. Note that we only use data through 2014, during which
time all \ac{RCP} scenarios behave similarly and the choice of the scenario is
not expected to affect the results considerably. Such an extension is not
needed for \acs{CMIP}6 models as their historical simulations cover a longer
time period until 2014. We quantify the skill of the emergent constraints with
three metrics: the coefficient of determination $R^2$ of the linear
relationship, the statistical significance using a two-sided $t$-test based on
the Pearson correlation coefficient $r$ (see \cref{eq:02:t}), and the
constrained range of \ac{ECS} based on the constrained \ac{PDF} (see
\cref{eq:02:pdf_y_given_x0}).

@@

In this \namecref{sec:05:comparison_of_emergent_constraints} we describe and
discuss the 11 emergent constraints on \ac{ECS} summarized in
\cref{tab:05:overview_emergent_constraints} using \acs{CMIP}5 and \acs{CMIP}6
data
(\cref{subsec:05:bri,subsec:05:cox,subsec:05:lip,subsec:05:shd,subsec:05:shs,%
  subsec:05:shl,subsec:05:su,subsec:05:tih,subsec:05:tii,subsec:05:vol,%
  subsec:05:zha}) and provide a best estimate for \ac{ECS} and statistical
significance of the 11 emergent constraints in
\cref{subsec:05:emergent_constraints_summary}. While most of these emergent
constraints have been derived using data from the \acs{CMIP}5 and/or
\acs{CMIP}3 ensembles, to our knowledge none of them has been evaluated on
the \acs{CMIP}6 ensemble so far. The results for the individual emergent
constraints described in the following are shown in
\cref{fig:05:bri_cox_lip,fig:05:shd_shl_shs,fig:05:su_tih_tii,fig:05:vol_zha}.
The left columns in these figures show the emergent relationships, including
the uncertainty of the linear regressions (blue and orange shaded areas; see
\cref{eq:02:spe}) and the uncertainty in the observations (gray shaded area;
see \cref{eq:02:pdf_obs}). The right columns show the \acp{PDF} of \ac{ECS} in
the original model ensemble (histogram) and the constrained distribution given
by the emergent constraints (blue and orange line; see
\cref{eq:02:pdf_y_given_x0}). \Cref{tab:05:overview_results} shows the
corresponding $66 \unit{\%}$ confidence intervals (\ie{} the
$\rangeunit{17}{83}{\%}$ intervals) of \ac{ECS} derived from the \acp{PDF}
given by \cref{eq:02:pdf_y_given_x0} and the $p$-values used to assess the
significance of the emergent relationships.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{ch05_paper_ecs/figs/zha.pdf}
  \caption[
    Emergent relationship ZHA for different subsets of \acs{CMIP}5 models.
  ]{
    Emergent relationship ZHA \autocite{Zhai2015} for different subsets of
    \acs{CMIP}5 models. Blue circles show the 15 \acs{CMIP}5 models used in the
    original publication (except for \acs{CESM}1-CAM5). The solid blue line and
    blue shaded area show the emergent relationships evaluated on these models
    including the uncertainty range. In our study, we added 11 more \acs{CMIP}5
    models (red circles). The corresponding emergent relationship that
    considers all available \acs{CMIP}5 models is shown in red colors. This
    relationship shows a considerably lower coefficient of determination
    ($R^2$) and higher $p$-value than the relationship using the original
    subset of \acs{CMIP}5 models. The vertical dashed line and shaded area
    correspond to the observational reference, and the horizontal dashed lines
    show the corresponding constraints on the \acf{ECS} using this observation.
    \AdaptedFrom{Schlund2020a}.
  }
  \label{fig:05:zha}
\end{figure}

\textcite{Zhai2015} focus on the variations of \acp{MBLC}, which largely
contribute to the shortwave cloud feedback and thus to the uncertainty in
modeled \ac{ECS}. Their central quantity is the response of the \ac{MBLC}
fraction to changes in the \ac{SST} in subtropical oceanic subsidence regions
for both hemispheres ($\rangeunit{20}{40}{\degree}$). On short (seasonal) and
long (centennial under a forcing) time scales, this quantity is well correlated
with \ac{ECS} among an ensemble of \acs{CMIP}3 and \acs{CMIP}5 models. Together
with observations of cloud fraction from CloudSat/CALIPSO \autocite{Mace2009},
\ac{SST} from AMSRE \ac{SST} \autocite{AMSRE2011}, and vertical velocity from
ERA-Interim \autocite{Dee2011}, the seasonal response of \ac{MBLC} fraction to
changes in \ac{SST} forms an emergent constraint on \ac{ECS}. We assess a $66
\unit{\%}$ \ac{ECS} range of $\pmrangeunit{3.35}{0.74}{K}$ for \acs{CMIP}5
($R^2 = 0.05$) and $\pmrangeunit{3.79}{0.67}{K}$ for \acs{CMIP}6 ($R^2 =
0.62$). In their original publication, \textcite{Zhai2015} find \iac{ECS} range
of $\pmrangeunit{3.90}{0.45}{K}$ (standard deviation) for a combination of
\acs{CMIP}3 and \acs{CMIP}5 models. In terms of statistical significance, the
results of the ZHA constraints are somewhat surprising: although \acs{CMIP}5
data (in combination with \acs{CMIP}3 data) has successfully been used in the
original publication, our approach finds that the statistical significance of
the emergent relationship is much higher in the unseen \acs{CMIP}6 ensemble ($p
< 0.0001$) than in the previously available \acs{CMIP}5 ensemble ($p =
0.2567$). The ZHA constraint is the only emergent constraint analyzed here that
shows this extreme behavior (only one other constraint, SHS, shows a slightly
higher significance in \acs{CMIP}6; all other constraints show lower
significances in \acs{CMIP}6). The reason for the erratic skill in \acs{CMIP}5
is the set of climate models used. For our analysis, we use 11 additional
\acs{CMIP}5 models that have not been used in the original publication
(ACCESS1-0, ACCESS1-3, bcc-csm1-1, bcc-csm1-1-m, CCSM4, GFDL-ESM2G, GFDL-ESM2M,
IPSL-CM5A-MR, IPSL-CM5B-LR, MPI-ESM-MR, and MPI-ESM-P). Due to a lack of
publicly available data, the model \acs{CESM}1-CAM5 that is used in the
original publication is not included in our analysis. The effect of choosing
different subsets of \acs{CMIP}5 models on the emergent relationship is
illustrated in \cref{fig:05:zha}. Using the original \acs{CMIP}5 models from
the original publication gives a considerably higher correlation ($R^2 = 0.38$)
than using all available \acs{CMIP}5 models ($R^2 = 0.05$). This result shows a
strong dependency of this emergent constraint on the subset of climate models
used. Nonetheless, the performance on \acs{CMIP}6 models is, surprisingly, the
best of all the constraints and much better than on either subset of
\acs{CMIP}5 models.

\subsection{Constrained \acs{ECS} Ranges and Statistical Significance of the 11
  Emergent Constraints}
\label{subsec:05:emergent_constraints_summary}

\begin{table}[!b]
  \centering
  \begin{tabular}{p{0.06\columnwidth} p{0.34\columnwidth} y{0.12} y{0.12}
      y{0.1} y{0.1}}
    \toprule
    Label & \ecreshead{\acs{ECS}}{(original publication)} &
    \ecreshead{\acs{ECS} [$\si{K}$]}{(\acs{CMIP}5)} & \ecreshead{\acs{ECS}
      [$\si{K}$]}{(\acs{CMIP}6)} & \ecreshead{$p$}{(\acs{CMIP}5)} &
    \ecreshead{$p$}{(\acs{CMIP}6)} \\
    \midrule
    BRI & most likely $4.0 \unit{K}$, $< 2.30 \unit{K}$ very unlikely ($90
    \unit{\%}$ confidence) & 3.72
    \pm 0.59 & 4.32 \pm 1.07 & 0.0005 & 0.0355 \\
    COX & $\pmrangeunit{2.8}{0.6}{K}$ & 3.03 \pm 0.73 & 3.71 \pm 1.09 & 0.0032
    & 0.5415 \\
    LIP & no best estimate given & 2.97 \pm 0.75 & 3.75 \pm 1.11 & 0.0228 &
    0.6791 \\
    SHD & none --- see SHL & 3.65 \pm 0.64 & 3.77 \pm 1.06 & 0.0037 & 0.2805 \\
    SHL & most likely $4 \unit{K}$, lower limit $3 \unit{K}$ & 3.42 \pm 0.65 &
    3.67 \pm 1.06 & 0.0002 & 0.0138 \\
    SHS & none --- see SHL & 3.07 \pm 0.73 & 3.48 \pm 1.07 & 0.0647 & 0.0396 \\
    SU & most likely $4 \unit{K}$, lower limit $3 \unit{K}$ & 3.30 \pm 0.88 &
    3.77 \pm 1.35 & 0.1676 & 0.1935 \\
    TIH & most likely $4.0 \unit{K}$ & 3.88 \pm 0.75 & 4.15 \pm 1.10 & 0.0089
    & 0.1348 \\
    TII & most likely $4.0 \unit{K}$ & 3.87 \pm 0.67 & 3.84 \pm 1.09 & 0.0013
    & 0.8236 \\
    VOL & $\pmrangeunit{3.6}{0.4}{K}$ (\stddev{}) & 3.74 \pm 0.64 & 4.21 \pm
    1.04 & 0.0004 & 0.0056 \\
    ZHA & $\pmrangeunit{3.90}{0.45}{K}$ (\stddev{}) & 3.35 \pm 0.74 & 3.79 \pm
    0.67 & 0.2567 & < 0.0001 \\
    \bottomrule
  \end{tabular}
  \caption[
    Overview of the constrained \acf{ECS} ranges and $p$-values for all 11
    analyzed emergent constraints.
  ]{
    Overview of the constrained \acf{ECS} ranges and $p$-values for all 11
    analyzed emergent constraints. If not further specified, the uncertainty
    ranges correspond to the $66 \unit{\%}$ confidence intervals
    ($\rangeunit{17}{83}{\%}$). For \acs{CMIP}5 and \acs{CMIP}6, these are
    evaluated from the \acl{PDF} given by \cref{eq:02:pdf_y_given_x0} (see also
    the right columns of \cref{fig:05:bri_cox_lip,fig:05:shd_shl_shs,%
      fig:05:su_tih_tii,fig:05:vol_zha}). Note that even though \acs{CMIP}5
    models have been used for some constraints in the original publications,
    the constrained ranges in the second and third column might differ due to
    the use of a different subset of climate models (in this study, we use
    output from all \acs{CMIP} models that is publicly available; see
    \cref{tab:app:a:cmip5_emergent_constraints_part1,%
      tab:app:a:cmip5_emergent_constraints_part2,%
      tab:app:a:cmip6_emergent_constraints_part1,%
      tab:app:a:cmip6_emergent_constraints_part2} for details). The $p$-values
    describing the significances of the emergent relationships are defined as
    the probability to obtain an absolute correlation coefficient $\abs*{r}$
    or higher under the null hypothesis that the true underlying correlation
    coefficient between the predictor and \acs{ECS} is zero. Smaller
    $p$-values point to higher significance and vice versa (see
    \cref{subsec:02:emergent_constraints} for details).
    \AdaptedFrom{Schlund2020a}.
  }
  \label{tab:05:overview_results}
\end{table}
